|

### 2024-10-28 output/seminar-slideshow.qmd
Add IRS contour plot

::: columns
::: column
```{r mirt-model}
#| fig-width:  5
#| fig-height: 5
PROB_AXIS_2D <- seq(-3, 3, by = .1)

mirt_item <- tribble(
  ~a_1, ~a_2, ~d,
  2,    1,    -1.5
)

@@

mirt_item_probs |>
  plot_ly(
    x = ~PROB_AXIS_2D,
    y = ~PROB_AXIS_2D,
    z = ~mirt_prob_surface,
    colorscale = list(c(0, 1), PALETTE_BLUE["normal"] |> rep(2)),
    type = 'surface',
    showscale = FALSE,
    hoverinfo = 'none'
  ) |>
  layout(
    scene = list(
      xaxis = list(title = "<i>θ</i><sub>1</sub>"),
      yaxis = list(title = "<i>θ</i><sub>2</sub>"),
      zaxis = list(title = "P(I<sub>k</sub> = 1)"),
      camera = list(
        center = list(z = -.2),
        eye = list(x = -.12, y = -1.8, z = 1)
      )
    )
  ) |>
  config(
    displayModeBar = FALSE,
    scrollZoom = FALSE,
    mathjax = 'cdn'
  )
```

:::

::: column
:::
:::

>>>>

::: columns
::: column
```{r mirt-model-irs-3d}
#| fig-width:  5
#| fig-height: 5
PROB_AXIS_2D <- seq(-3, 3, by = .1)

mirt_item <- tribble(
  ~a_1, ~a_2, ~d,
  1,    0.5,  -0.5
)

@@

plot_ly(
  x = ~PROB_AXIS_2D,
  y = ~PROB_AXIS_2D,
  z = ~mirt_prob_surface,
  colorscale = list(c(0, 1), PALETTE_BLUE["normal"] |> rep(2)),
  type = 'surface',
  showscale = FALSE,
  hoverinfo = 'none'
) |>
  layout(
    scene = list(
      xaxis = list(title = "<i>θ</i><sub>1</sub>"),
      yaxis = list(title = "<i>θ</i><sub>2</sub>"),
      zaxis = list(title = "P(I<sub>k</sub> = 1)"),
      camera = list(
        center = list(z = -.2),
        eye = list(x = -.12, y = -1.8, z = 1)
      )
    )
  ) |>
  config(
    displayModeBar = FALSE,
    scrollZoom = FALSE,
    mathjax = 'cdn'
  )
```
:::

::: column
```{r mirt-model-irs-3d}
#| fig-width:  5
#| fig-height: 5

mirt_item_probs |>
  ggplot(mapping = aes(trait_1, trait_2, z = prob)) +
  geom_contour() +
  scale_x_continuous(
    minor_breaks = NULL,
    limits = range(PROB_AXIS_2D),
    expand = expansion()
  ) +
  scale_y_continuous(
    minor_breaks = NULL,
    limits = range(PROB_AXIS_2D),
    expand = expansion()
  ) +
  coord_fixed() +
  labs(x = "*&theta;*~1~", y = "*&theta;*~2~") +
  theme(
    axis.title       = element_markdown(),
    axis.title.y     = element_markdown(angle = 90),
    panel.grid.major = element_line(linetype = "17"),
  )

```
:::
:::
